### 2015-07-08 narrative/proposed-work.tex

\underline{Principle 2}: {\bf Predictable performance and quality of data in the SSIO layer} needs to be
established so more science can be done on the exascale systems. Without
predictable performance, the I/O layer performance must be guessed by the
users, which quite often mean that science is not performed well.

>>>>

\underline{Principle 2}: {\bf Predictable performance and quality of data in the SSIO layer} needs to be
established so more science can be done on the exascale systems. Without
predictable performance, the I/O layer performance must be guessed by the
users, which quite often means that science is not performed well.

Our work is to take much of the ``magic'' and ``tricks''
away from optimizations necessary for users to understand to gain optimizations
on current file systems, and provide a systematic approach to describing enough
of their intentions and knolwedge from the {\it user} space along with much
of the hidden knowledge of the underlying storage layers. For example,
   ADIOS contains most of the ``best practices'' for I/O optimizations for
   each file system, and as users place more knowledge into ADIOS, ADIOS
   can make optimizations. This becomes much more difficult as users want to
   describe more about the storage hiearchy and more about the priorities of
   different chunks of data. Our research is aimed to allow users to simply
   describe this and get the descriptions of system knowledge so that the
   best optimizations can be made.
